The Driving Forces Behind API Evolution

### 2015-05-20 thesis/paper.tex
impl pract

By analysing the API based on Lehman's laws, we were able to find that the law of Conservation of Organisational Stability did not apply to the API examined in this study. Our results suggest that the opposite of what the law says in its current form is closer to the truth (!!!reword) for APIs. Since we only studied one API, we cannot safely refute the law or propose a new formulation of it. We do, however, believe that academia should be wary of assuming that this law is true for APIs.

\subsection{Implications for Practitioners}
The changes introduced to the API are mainly based on the expertise and experiences of the API architects at the case company. There has not been a scientific approach to maintaining the system and the knowledge from academia has not directly affected the way that the API's evolution has been managed. With our work, we hope to provide a new angle of analysis

------------------------------------------------------------------------

>>>>

By analysing the API based on Lehman's laws, we were able to find that the law of Conservation of Organisational Stability did not apply to the API examined in this study. Our results suggest that the opposite of what the law says in its current form is closer to the truth (!!!reword) for APIs. Since we only studied one API, we cannot safely refute the law or propose a new formulation of it. We do, however, believe that academia should be wary of assuming (!!!reword) that this law is true for APIs.

\subsection{Implications for Practitioners}
The changes introduced to the API are mainly based on the expertise and experiences of the API architects at the case company. There has not been a scientific approach to maintaining the system and the knowledge from academia has not directly affected the way that the API's evolution has been managed. With our work, we hope to provide a new type of insight (!!!reword) into how the API is maintained. Our analysis of the API based on Lehman's laws should further assure that the case company is moving the evolution of the API in the right direction. With our research, we leave a challenge (!!!reword) for the case company in how to tackle challenges related to the law of Conservation of Organisational Stability. Determining if the benefits of continuously and frequently updating the API outweigh the negative effects that these updates could have on the application developers, we leave up to the company (!!!reword so that it doesnt sound negative)

An alternative way of addressing this problem could be by including the application developers in the feedback loop.

----------------------------------------------------------------------
